Forecasting the black Sigatoka development rate:\\ A comparison of machine learning techniques

### 2017-04-30 methodology.tex
30-4 00-52

\begin{itemize}
\item Patrones de semanas: Se formaron patrones desde tres semanas continuas
de observación para predecir una semana adelante, hasta doce semanas de
observación para predecir tres semanas adelante. Por tanto, $n\times{}m$, 
with $n=1\ldots{}12$ and $m=1\ldots{}3$.

\item techniques: support vector regression with the kernels linear,
  gaussian and sigmoid; echo state networks; ordinary least squares
  linear regression and elastic-net regression.

\item Variables included in the model:
\begin{itemize}
\item All variables.
\item From the set $\{ \overline{T}_{a} , \overline{H}, P ,
  \overline{W} \}$ use the subsets with one, two, three or four
  elements. These variables have the largest impact on the disease
  development \citep{MarinVargas1995}.
\end{itemize}

\end{itemize}

>>>>

\begin{itemize}
\item Patrones de semanas: Se formaron patrones desde tres semanas continuas
de observación para predecir una semana adelante, hasta doce semanas de
observación para predecir tres semanas adelante. Por tanto, $n\times{}m$ combinations, 
with $n=1\ldots{}12$ and $m=1\ldots{}3$.

\item Techniques: Se utilizaron las siguientes técnicas, revisando el espacio
paramétrico especificado a continuación:
\begin{itemize}
\item SVR with linear kernel: $C$ $[0.001, 1, 10, 100, 1000]$, $epsilon$ $[0.0, 0.4, 0.9]$.
\item SVR with gaussian kernel: $C$ $[0.001, 1, 10, 100, 1000]$, $epsilon$ $[0.0, 0.4, 0.9]$,
$gamma$ $[0.0, 0.4, 0.9]$.
\item SVR with sigmoid kernel: $C$ $[0.001, 1, 10, 100, 1000]$, $epsilon$ $[0.0, 0.4, 0.9]$,
$gamma$ $[0.0, 0.4, 0.9]$, $coef0$ $[0.0, 0.5, 5, 10]$.
\item Echo state networks: $LeakingRate$ $[0.02 .. 0.9]$, $neurons$ $[1\% .. 90\%]$ de la 
cardinalidad del training set, $InitLen$ $[ 0.1 .. 0.8 ]$.
\item Ordinary least squares linear regression: No parameters.
\item Elastic-net regression: $alpha$ $[0 .. 0.9]$, $l1\_ratio$ $[0 .. 1.0]$.
\end{itemize}

\item Variables included in the model:
\begin{itemize}
\item All variables.
\item From the set $\{ \overline{T}_{a} , \overline{H}, P ,
  \overline{W} \}$ use the subsets with one, two, three or four
  elements. These variables have the largest impact on the disease
  development \citep{MarinVargas1995}.
\end{itemize}
\end{itemize}

### 2017-04-30 results.tex
30-4 00-52

In this section we present the main results for phase and their discussion.

{\bf Phase one }

@@

\begin{figure}[H] 
 \centering
 \includegraphics[scale=.5]{Phase_one_Best_R2_for_each_algortihm}
 \caption{Phase one - Best $R^2$ for each algorithm} 
 \label{figura4} 
\end{figure}

@@

\begin{figure}[H] 
 \centering
 \includegraphics[scale=.5]{Phase_one_Best_R2_for_each_number_of_observation_range_in_the_patterm}
 \caption{Phase one - Best $R^2$ for each observation range} 
 \label{figura5} 
\end{figure}

@@

\begin{figure}[H] 
 \centering
 \includegraphics[scale=.5]{Phase_one_Best_R2_for_variables}
 \caption{Phase one - Best $R^2$ for each variable combination} 
 \label{figura6} 
\end{figure}

@@

{\bf Phase two }

In the second phase, the best configurations obtained in phase one were used to validate with the last 50 and 100 weeks.

\figref{figura8} shows the best $R^2$ for each algorithm in the experiment. Results are group by farm. Even if linear models continue with good $R^2$, Echo State Networks improve their scores because in $50$ and $100$ last weeks validation, we are in presence of climate change, then the behaviour is less lineal.

\begin{figure}[H] 
 \centering
 \includegraphics[scale=.5]{Phase_two_Best_R2_for_each_algortihm}
 \caption{Phase two - Best $R^2$ for each algorithm} 
 \label{figura8} 
\end{figure}

\figref{figura9} presents, for one, two and three weeks ahead, the best $R^2$. Results are group by farm. The results confirms that, in general, to predict one week ahead is better than two weeks ahead, two than three and so on, this for both farms.

\begin{figure}[H] 
 \centering
 \includegraphics[scale=.5]{Phase_two_Best_R2_for_each_number_of_observation_range_in_the_patterm}
 \caption{Phase two - Best $R^2$ for each observation range} 
 \label{figura9} 
\end{figure}

\figref{figura10} shows the best $R^2$ for each variables combination. Results are group by farm. This results confirm that $\overline{T}_{a}$ and the combination of $\overline{T}_{a}$ with $\overline{W}$, in both farms are the best variables combinations.

\begin{figure}[H] 
 \centering
 \includegraphics[scale=.5]{Phase_one_Best_R2_for_variables}
 \caption{Phase two - Best $R^2$ for each variable combination} 
 \label{figura10} 
\end{figure}

\figref{figura11} shows the Pareto frontier for each farm with respect to $R^2$ and $RMSE$.  You can note that the behaviour of $R^2$ and $RMSE$ is similar to the phase one.

\begin{figure}[H] 
 \centering
 \includegraphics[scale=.8]{Phase_two_R2_RMSE}
 \caption{Phase two - Pareto frontier for $R^2$ and $RMSE$} 
 \label{figura11} 
\end{figure}

In phase two, the Pareto frontier for the La Rita farm is composed by 2 elements. The \tablename $.$\ref{tabla4} shows the composition about variables and observation ranges.

\begin{table}[h] 
\caption{Composition of the Pareto frontier - La Rita - Phase two} 
\label{tabla4} 
\centering
\begin{tabular}{c|c|c|c|c} 
\hline
\bfseries Variable & \bfseries Observation range & \bfseries Quantity & \bfseries Max $R^2$ & \bfseries Min $RMSE$\\ 
\hline\hline 
All & 1 to 1  & 2 & 69.33\% & 353.33 \\
\hline
\end{tabular} 
\end{table}

In 28 Millas Farm, the Pareto frontier is composed by 1 element. The \tablename $.$\ref{tabla5} details the result.

\begin{table}[h] 
\caption{Pareto frontier - 28 Millas - Phase two} 
\label{tabla5} 
\centering
\begin{tabular}{c|c|c|c|c} 
\hline
\bfseries Variable & \bfseries Observation range & \bfseries Quantity & \bfseries Max $R^2$ & \bfseries Min $RMSE$\\ 
\hline\hline 
Pair $\overline{T}_{a}$ $P$ & 1 to 1 & 1 & 61.36\% & 339.89 \\
\hline
\end{tabular} 
\end{table}

Again, similar to phase one, we can conclude that the best configuration in both farms is to consider the climate and the evolution stage of the current week to predict the evolution stage of the next week, one week to predict one week ahead with combinations of variables listed above.

>>>>

In this section the main results are presented and discussed.

@@

\begin{figure}[H] 
 \centering
 \includegraphics[scale=.5]{2017-01-15-Algorithms-R2}
 \caption{Phase one - Best $R^2$ for each algorithm} 
 \label{figura4} 
\end{figure}

@@

\begin{figure}[H] 
 \centering
 \includegraphics[scale=.5]{2017-01-15-Periods-R2}
 \caption{Phase one - Best $R^2$ for each observation range} 
 \label{figura5} 
\end{figure}

@@

\begin{figure}[H] 
 \centering
 \includegraphics[scale=.5]{2017-01-15-Variables-R2}
 \caption{Phase one - Best $R^2$ for each variable combination} 
 \label{figura6} 
\end{figure}

@@
